Did WW2 Produce an Equivalent to a Modern Computer?

### 2017-04-20 Draft 2/Master.tex
Included bibliography
Added remaining files, included in Master.pdf, commented out sections for
testing
Removed comments and updated lambda rojas reference
Colossal changes to all sections
Added referencing, changed language of turing machines, more detailed
intros&concns
Introduction
Moving from nothing to something

\documentclass {article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{subfiles}
\usepackage{blindtext}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{multirow, bigdelim}
\usepackage{hhline}
\usepackage{tabu}	
\usepackage[bb=boondox]{mathalfa}
\usepackage{yfonts}
\usepackage{cleveref}
\usepackage{listings}

@@

\begin{document}
\pagenumbering{roman}
\maketitle
\tableofcontents
\clearpage

@@

\subfile{"Section 3 - Universality"}

\end{document}

>>>>

\documentclass {article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{subfiles}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{blindtext}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{hhline}
\usepackage{listings}
\usepackage[bb=boondox]{mathalfa}
\usepackage{multirow, bigdelim}
\usepackage{tabu}
\usepackage{yfonts}

@@

\crefname{section}{§}{§§}
\Crefname{section}{§}{§§}

\begin{document}
\pagenumbering{roman}
\maketitle
\tableofcontents
\clearpage
\textit{TODO: introduction - stating aim of checking whether computers produced during and after WW2 were 'computers'}

Computation rules the modern world - from the internet to the rise of automated labour, today's humanity puts colossal value in the hands of computers, taking them for granted as the remarkable machines they are. However, the fundamental ideas of computation and calculation lying alongside the transistors and silicon at the heart of this revolution are no less remarkable in themselves, primarily down to their simplicity. Furthermore, it is difficult for any modern computer user to see how basic electronics can operate the tasks a computer can perform. Therefore, I feel the natural way to shed light on this question is to look at the earliest and simplest computers, what they could do and what was distinctive about them.

The most significant problem in answering this question is the actual definition of `computer'. In the early 20th Century, prior to developments in this field, any human which evaluated statements through computation was known, logically, as a `computer'. As such, we must explore the qualities that an entity - human, machine or other - must have to be able to perform computation.

\textit{(Leibniz's ideas of computation, all effectively computable statements could be expressed in terms of a simple language \& a method to evaluate these statements - highlighting ideas of solving problems)}

Therefore, in order for a machine to be called a `computer', it must be able to evaluate any member of a set of computable functions. However, this is an abstract notion - to clarify it, we must define a simple language to define computable functions, and find a simple method to evaluate them. We shall explore the two most common methods - the abstract $\lambda$-calculus and the

@@

\subfile{"Section 3 - Universality"}
\bibliography{bibliography}
\bibliographystyle{unsrt}
\end{document}

### 2017-04-20 Draft 2/Section 3 - Universality.tex
Introduction
Moving from nothing to something

First, we must define what we actually mean by a description table - we shall do this by describing a standard form for these tables. Looking at the first table described, we can see that any transition function follows a similar format: E; [E, R]; [E, L]; P\textit{a}; [ P\textit{a}, R]; [ P\textit{a}, L] or no entry at all. More complex transition functions such as those found in later tables can always be put into one of these forms through the addition of intermediary states which are called in sequence.

>>>>

First, we must define what we actually mean by a description table - we shall do this by describing a standard form for these tables, as shown by Turing in \cite{turing1936computablenumbers}. Looking at the first table described, we can see that any transition function follows a similar format: E; [E, R]; [E, L]; P\textit{a}; [ P\textit{a}, R]; [ P\textit{a}, L] or no entry at all. More complex transition functions such as those found in later tables can always be put into one of these forms through the addition of intermediary states which are called in sequence.
